Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2015-09-23 Docs/TODAES/paper.tex
modifications in figures and journal structure

\usepackage{color}
\usepackage{multirow}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{booktabs}
\usepackage{tabu,xcolor,colortbl}
\usepackage{rotating}
\usepackage{amsmath,array}    
\usepackage[utf8]{inputenc} 
\DeclareUnicodeCharacter{FB01}{fi} %Caracter especial
\usepackage{graphicx} %Imagens
\usepackage{listings} % Codes
\usepackage{tabularx} % in the preamble
\usepackage{mathtools} % Serve para as equacoes
\usepackage{cite}
\usepackage{hyphenat}
\usepackage[english]{babel}

@@

There is no single method available for efficiently solving all optimization problems~\cite{Rao2009}. The most well-known technique is linear programming, which is an method applicable for the solution of problems in which the objective function and the constraints appear as linear functions of the decision variables. A particular case of linear programming is ILP, in which the variables can assume just integer values. Eq.~\ref{linear-programming-problem} shows a typical linear programming problem, where $A$ and $b$ are vectors or matrixes that describe the constraints
\begin{equation}
\label{linear-programming-problem}
  minf^t x \: such \; that  = 
  \begin{cases}
    A.x \leq b, \\ 
    Aeq.x = beq, \\ 
    x \geq 0.
  \end{cases}
\end{equation}

In some cases, the time to find a solution using ILP is impractical. Even with the use of powerful computers, a problem can take hours before an optimal solution is reached. If the optimization problem is complex, some heuristics can be used to solve the same problem faster, {\it e.g.}, those used in the GA~\cite{Rao2009}. The only drawback is that the found solution may not be the global minimum or maximum. Alternatively, tools such as $\nu$Z and ESBMC can be used to solve optimization problems so that the global minimum or maximum solution is found. The following sections describe the main features of $\nu$Z and ESBMC tools.

@@

Fig.~\ref{ESBMC-Architecture} shows the current ESBMC architecture, which consists of the C/C$++$ parser, GOTO Program, GOTO Symex, and SMT solver ~\cite{Ramalho2013}. In particular, ESBMC compiles C/C$++$ code into equivalent GOTO\hyp{}programs ({\it i.e.}, control-flow graphs) using a gcc-compliant style. GOTO-programs can then be processed by the symbolic execution engine, called GOTO Symex, where two recursive functions compute the constraints ($C$) and properties ($P$); finally, it generates two sets of equations (i.e.,\:$C \land \neg P$ ), which are checked for satisfiability by an SMT solver. The main factor for ESBMC to use only a single-core relies on its back-end (i.e., SMT Solver). Currently, the SMT solvers supported by ESBMC are: Z3~\cite{DeMoura2008}, Boolector~\cite{Brummayer2009}, MathSAT~\cite{Barrett2011}, CVC4~\cite{Bozzano2005}, and Yices~\cite{Dutertre2014}. Most of them do provide neither multi-threaded support nor a parallel version to solve the generated SMT equations.
%
\begin{figure}[ht]
	\centering
  \includegraphics[scale=0.9]{figures/esbmc-arch-new.pdf} 
	\caption{ESBMC Architecture.}
	\label{ESBMC-Architecture}
\end{figure}

@@

\begin{lstlisting}[caption=OpenMP basic sample.]
01.  int i;
02.  #pragma omp parallel for
03.  for (i = 0; i < 10; i++)
04.      a[i] = 2 * i;
\end{lstlisting}

In the above example, the for loop is executed in parallel. Each iteration of the loop is executed in a separated thread; and each thread may use an idle processor. There is also a way to specify critical regions, which is a code block that is guaranteed to be executed by a single thread at a time. To create a critical region, the ``\#pragma omp critical'' directive is used.

@@

\begin{lstlisting}[caption=Example of SMT formula using $\nu$Z., label=vZ]
1. (declare-const K Int) 
2. (declare-const W Int)
3. (assert (< K 2)) 
4. (assert (< (- W K) 1))
5. (maximize (+ K W)) 
6. (check-sat)
\end{lstlisting}

Fig.~\ref{vZ-Architecture} shows the $\nu$Z architecture. Initially, the SMT formula with objectives is converted to $0-1$ constraints, which leads to a Pseudo-Boolean Optimization (PBO)~\cite{Barth1995,Vasco2005}. If there are many objective functions, $\nu$Z invokes OptSAT for arithmetic or MaxSAT for soft constraints. For constraints using real values, $\nu$Z combines linear arithmetic objectives and uses only one instance of OptSMT. When ``soft constrains'' is used in the mode `` lexicographic'', $\nu$Z invokes MaxSAT using multiple calls for its engine.
%
\begin{figure}[ht]
	\centering
  \includegraphics[width=0.49\textwidth, height=95px]{figures/vzArch.png} 
	\caption{$\nu$Z Architecture extracted from~\cite{Bjorner2015}.}
	\label{vZ-Architecture}
\end{figure}

@@

Based on Arat\'o {\it et al.}~\cite{Arato2003}, is called a hardware-software partition if it is a bipartition of $V:P = (V_h, V_s)$, where $V_h \cup V_s = V$  and $V_h \cap V_s = 0$. The crossing edges are $E_p = \{(V_i,V_j):V_i \in V_s, V_j \in V_h$ or $v_i \in V_h, v_j \in V_s $. The hardware cost of $P$ is given by Eq.~\ref{hardware-costs}
%
\begin{align}
\label{hardware-costs}
H_p  &= \Sigma_{v_i \in V_H} h_i
\end{align}
%
\noindent and the software cost of $P$ ({\it i.e.}, software cost of the nodes and the communication cost) is given by Eq.~\ref{software-communication-costs}
%
%  S_p &= \Sigma_{\left(v_i \;\in\; V_s\right)} s_i + \Sigma_{(v_i,v_j) \in\; %E_p}\; c(V_i, V_j).
\begin{align}
\label{software-communication-costs}
  S_p &= \Sigma_{v_i \in V_s}\:s_i + \Sigma_{(v_i,v_j)\in\:E_p} c(V_i,V_j)
\end{align}

Three different optimization and decision problems can be defined. In this paper, the focus is on the case that $ S_0 $ is given, i.e., to find a $P$ HW-SW partitioning so that $ S_p \leq S_0 $ and $ H_p $ is minimal ({\it i.e.}, system with hard real-time constraints). Based on Equations~\ref{linear-programming-problem} and~\ref{software-communication-costs}, the constraints can be reformulated as 
%
\begin{align}
\label{hw-sw-partitioning}
s\left(1-x\right) + c|E_x| \leq S_0, 
\end{align}
%
\noindent where $x$ represents the decision variable. Concerning the complexity of this problem, Arat\'o {\it et al.}~\cite{Arato2003} demonstrate that it is NP-Hard~\cite{Cormem}.

@@

\begin{lstlisting}[caption=Pseudocode describing sequential ESBMC., label={Pseudocode-describing-ESBMC}, mathescape]
01. Initialize Variables 
02. Declare number of nodes and edges
03. Declare hardware cost of each node as array (h)
04. Declare software cost of each node as array (s)
05. Declare communication cost of each edge (c)
06. Declare the initial software cost of ($S_{0}$)
07. Declare transposed incidence matrix graph G (E)
08. Define the solutions variable ($X_{i}$ ) as Boolean
09. main {
10.  for TipH = 0 to Hmax do {
11.   populate $X_{i}$ with nondeterministic/test values
12.   Calculate s(1-x)+c|$E_{x}$| and store at variable
13.   Requirement isued by Assume (Variable <= $S_{0}$)
14.   Calculate Hp cost Based on value tested of $X_{i}$
15.   Violation check with Assert($H_{p}$ > TipH)
16.  }
17. }
\end{lstlisting}

@@

To optimize the CPU resources utilization without modifying the underlying SMT Solver, the Open Multi-Processing (OpenMP) library~\cite{Dagum1998} is used in this present work as a front-end for ESBMC. Fig.~\ref{ESBMC-Multi-core} shows our first approach called ``Multi-core ESBMC''.
%
\begin{figure}[ht]
	\centering
  \includegraphics[scale=0.75]{figures/esbmc-parallel.pdf} 
	\caption{ESBMC-SS Approach.}
	\label{ESBMC-Multi-core}
\end{figure}

@@

\begin{figure}[ht]
	\centering
  \includegraphics[scale=0.75]{figures/esbmc-parallel.png} 
	\caption{ESBMC-PS Approach. }
	\label{ESBMC-Multi-core-Optimized-Sequential-Approach}
\end{figure}

@@

The most optimized approach applies a parallelized binary search to reduce the amount of steps to be executed in order to find the optimal solution. A controller is designed to return the step to be executed so that the number of verification runs are substantially reduced. The parallelized binary search accomplishes this by splitting the domain of possible values into intervals and then by returning the middle of the largest interval so that two new intervals are created.
%
\begin{figure}[ht]
	\centering
  \includegraphics[scale=0.75]{figures/esbmc-parallel-Controler.png} 
	\caption{ESBMC-PB Approach.}
	\label{ESBMC-Binary-Approach}
\end{figure}

As an example, given a problem of domain from $1$ to $20$ (see Fig.~\ref{Binary-Step-Calculation}), we firstly create an initial interval from $1$ to $20$. When the next available core asks for a step to be executed, the controller obtains the largest interval, {\it i.e.}, $\left[1,20\right]$, divides it by two, which creates two new intervals ({\it i.e.}, $\left[1,9\right]$ and $\left[11,20\right]$), and returns the middle of the original interval ({\it i.e.}, $10$). The controller also checks whether an interval has less than two elements to avoid creating empty or invalid intervals.
%
\begin{figure}[ht]
	\centering
  \includegraphics[width=0.49\textwidth, height=75px]{figures/Fig4.png}
	\caption{Binary Step Calculation.}
	\label{Binary-Step-Calculation}
\end{figure}

@@

\begin{lstlisting}[caption=Steps Calculation using Intervals.,label=Steps-Calculation-using-Intervals]
01. GetNextStep(){
02.  int largestChunk = -1;
03.  chunk largest;
04.  for each(chunk in chunks){
05.     if(chunk.right - chunk.left > largestChunk){
06.           largestChunk = chunk.right - chunk.left;
07.           largest = chunk;
08.     }
09.   }	
10.   chunks.remove(largest);	
11.   int median = largest.left + floor((largest.right - largest.left) / 2)
12.   if(median > 0){
13.      if(largest.right - largest.left > 1)
14.         chunks.add(new chunk(largest.left, median - 1));	
15.      if(largest.right != largest.left)
16.         chunks.add(new chunk(median + 1, largest.right);
17.    }
18.   return median;
19. }
\end{lstlisting}

Note that Algorithm~\ref{Steps-Calculation-using-Intervals} is called from each worker in order to get the next step to execute if it exists; otherwise, either zero or a negative number is returned.
From lines $4$ to $9$, the algorithm finds the largest interval. Then, from the line $10$ the largest interval is removed and the median is calculated in line $11$. After that, two new intervals are created, the left side (in line $14$) and the right side (in line $16$). At the end, the median is returned.

\begin{lstlisting}[caption=Worker sample.,label=worker-sample]
01. step = controller.GetNextStep();
02. int pid = ExecuteStep(step);
03. while(isRunning(pid)){
04.   if(!controller.isNeeded(step))
05.    kill(pid);
06. }     
\end{lstlisting}

Algorithm~\ref{worker-sample} describes how the worker starts and monitors ESBMC instances. The algorithm starts by retrieving the step to be executed from the controller (line $1$), then initiates the ESBMC instance and obtains the process \textit{id} from the forked process (line $2$). While the step is being executed, the controller checks whether this step is still needed (line $4$). If not, then the ESBMC instance is killed (line $5$) and the worker is free to initiate another step.

@@

\begin{lstlisting}[caption=Pseudocode describing $\nu$Z.,label=vZ-pseudocode, mathescape]
01.#Initialize Variables
02.  Create vZ context 
03.  Create binary vector (x)
04.  Declare number of nodes, edges and $S_{0}$
05.  Declare hardware cost of each node as array (h) 
06.  Declare software cost of each node as array (s)
07.  Declare communication cost of each edge (c)
08.  Declare transposed incidence matrix graph G (E)
09.#Arithmetic Expressions
10.  SC = s(1-x)
11.  CMC = c*|EX|
12.  Fobj =  x[i] * h[i]
13.#Assert Constraints
14.  Add constraints (SF + CMC <= $S_{0}$)
15.  Add constraints to minimize Fobj
16.  Check Model
17.  Print Result
\end{lstlisting}

@@

\begin{table}[h]
\caption {Description of Benchmarks.}
\small
\sffamily\footnotesize
\tabulinesep=6pt
\begin{tabular}[c]{m{1.5cm}m{0.8cm}m{0.8cm}m{3.8cm}}
  \toprule[1.5pt]
%  \head{Name} & \head{Nodes} & \head{Edges} & \head{Description}\\
  \midrule

>>>>

\usepackage{color}
\usepackage{multirow}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{booktabs}
\usepackage{tabu,xcolor,colortbl}
\usepackage{rotating}
\usepackage{amsmath,array}    
\usepackage[utf8]{inputenc} 
\DeclareUnicodeCharacter{FB01}{fi} %Caracter especial
\usepackage{graphicx} %Imagens
\usepackage{listings} % Codes
\usepackage{tabularx} % in the preamble
\usepackage{mathtools} % Serve para as equacoes
\usepackage{cite}
\usepackage{hyphenat}
\usepackage[english]{babel}
\usepackage[skip=\baselineskip]{caption}
\captionsetup[lstlisting]{font={small,tt}}

@@

There is no single method available for efficiently solving all optimization problems~\cite{Rao2009}. The most well-known technique is linear programming, which is an method applicable for the solution of problems in which the objective function and the constraints appear as linear functions of the decision variables. A particular case of linear programming is ILP, in which the variables can assume just integer values. Eq.~\ref{linear-programming-problem} shows a typical linear programming problem, where $A$ and $b$ are vectors or matrixes that describe the constraints

\begin{equation}
\label{linear-programming-problem}
  minf^t x \: such \; that  = 
  \begin{cases}
    A.x \leq b, \\ 
    Aeq.x = beq, \\ 
    x \geq 0.
  \end{cases}
\end{equation}

\vspace{5 mm}
In some cases, the time to find a solution using ILP is impractical. Even with the use of powerful computers, a problem can take hours before an optimal solution is reached. If the optimization problem is complex, some heuristics can be used to solve the same problem faster, {\it e.g.}, those used in the GA~\cite{Rao2009}. The only drawback is that the found solution may not be the global minimum or maximum. Alternatively, tools such as $\nu$Z and ESBMC can be used to solve optimization problems so that the global minimum or maximum solution is found. The following sections describe the main features of $\nu$Z and ESBMC tools.

@@

Fig.~\ref{ESBMC-Architecture} shows the current ESBMC architecture, which consists of the C/C$++$ parser, GOTO Program, GOTO Symex, and SMT solver ~\cite{Ramalho2013}. In particular, ESBMC compiles C/C$++$ code into equivalent GOTO\hyp{}programs ({\it i.e.}, control-flow graphs) using a gcc-compliant style. GOTO-programs can then be processed by the symbolic execution engine, called GOTO Symex, where two recursive functions compute the constraints ($C$) and properties ($P$); finally, it generates two sets of equations (i.e.,\:$C \land \neg P$ ), which are checked for satisfiability by an SMT solver. The main factor for ESBMC to use only a single-core relies on its back-end (i.e., SMT Solver). Currently, the SMT solvers supported by ESBMC are: Z3~\cite{DeMoura2008}, Boolector~\cite{Brummayer2009}, MathSAT~\cite{Barrett2011}, CVC4~\cite{Bozzano2005}, and Yices~\cite{Dutertre2014}. Most of them do provide neither multi-threaded support nor a parallel version to solve the generated SMT equations.

\begin{figure}[ht]
	\centering
  \includegraphics[scale=1.25]{figures/esbmc-arch-new.pdf} 
	\caption{ESBMC Architecture.}
	\label{ESBMC-Architecture}
\end{figure}

@@

\begin{lstlisting}[caption="OpenMP basic sample."]

01.  int i;
02.  #pragma omp parallel for
03.  for (i = 0; i < 10; i++)
04.      a[i] = 2 * i;
\end{lstlisting}

\vspace{3 mm}
In the above example, the for loop is executed in parallel. Each iteration of the loop is executed in a separated thread; and each thread may use an idle processor. There is also a way to specify critical regions, which is a code block that is guaranteed to be executed by a single thread at a time. To create a critical region, the ``\#pragma omp critical'' directive is used.

@@

\begin{lstlisting}[caption=Example of SMT formula using $\nu$Z., label=vZ]

1. (declare-const K Int) 
2. (declare-const W Int)
3. (assert (< K 2)) 
4. (assert (< (- W K) 1))
5. (maximize (+ K W)) 
6. (check-sat)
\end{lstlisting}

\vspace{3 mm}
Fig.~\ref{vZ-Architecture} shows the $\nu$Z architecture. Initially, the SMT formula with objectives is converted to $0-1$ constraints, which leads to a Pseudo-Boolean Optimization (PBO)~\cite{Barth1995,Vasco2005}. If there are many objective functions, $\nu$Z invokes OptSAT for arithmetic or MaxSAT for soft constraints. For constraints using real values, $\nu$Z combines linear arithmetic objectives and uses only one instance of OptSMT. When ``soft constrains'' is used in the mode `` lexicographic'', $\nu$Z invokes MaxSAT using multiple calls for its engine.

\begin{figure}[ht]
	\centering
  \includegraphics[scale=0.3]{figures/vzArch.png} 
	\caption{$\nu$Z Architecture extracted from~\cite{Bjorner2015}.}
	\label{vZ-Architecture}
\end{figure}

@@

Based on Arat\'o {\it et al.}~\cite{Arato2003}, is called a hardware-software partition if it is a bipartition of $V:P = (V_h, V_s)$, where $V_h \cup V_s = V$  and $V_h \cap V_s = 0$. The crossing edges are $E_p = \{(V_i,V_j):V_i \in V_s, V_j \in V_h$ or $v_i \in V_h, v_j \in V_s $. The hardware cost of $P$ is given by Eq.~\ref{hardware-costs}

\begin{align}
\label{hardware-costs}
H_p  &= \Sigma_{v_i \in V_H} h_i
\end{align}

\vspace{3 mm}
\noindent and the software cost of $P$ ({\it i.e.}, software cost of the nodes and the communication cost) is given by Eq.~\ref{software-communication-costs}

%  S_p &= \Sigma_{\left(v_i \;\in\; V_s\right)} s_i + \Sigma_{(v_i,v_j) \in\; %E_p}\; c(V_i, V_j).
\begin{align}
\label{software-communication-costs}
  S_p &= \Sigma_{v_i \in V_s}\:s_i + \Sigma_{(v_i,v_j)\in\:E_p} c(V_i,V_j)
\end{align}

\vspace{3 mm}
Three different optimization and decision problems can be defined. In this paper, the focus is on the case that $ S_0 $ is given, i.e., to find a $P$ HW-SW partitioning so that $ S_p \leq S_0 $ and $ H_p $ is minimal ({\it i.e.}, system with hard real-time constraints). Based on Equations~\ref{linear-programming-problem} and~\ref{software-communication-costs}, the constraints can be reformulated as

\begin{align}
\label{hw-sw-partitioning}
s\left(1-x\right) + c|E_x| \leq S_0, 
\end{align}

\vspace{3 mm}
\noindent where $x$ represents the decision variable. Concerning the complexity of this problem, Arat\'o {\it et al.}~\cite{Arato2003} demonstrate that it is NP-Hard~\cite{Cormem}.

@@

\begin{lstlisting}[caption=Pseudocode describing sequential ESBMC., label={Pseudocode-describing-ESBMC}, mathescape]

01. Initialize Variables 
02. Declare number of nodes and edges
03. Declare hardware cost of each node as array (h)
04. Declare software cost of each node as array (s)
05. Declare communication cost of each edge (c)
06. Declare the initial software cost of ($S_{0}$)
07. Declare transposed incidence matrix graph G (E)
08. Define the solutions variable ($X_{i}$ ) as Boolean
09. main {
10.  for TipH = 0 to Hmax do {
11.   populate $X_{i}$ with nondeterministic/test values
12.   Calculate s(1-x)+c|$E_{x}$| and store at variable
13.   Requirement isued by Assume (Variable <= $S_{0}$)
14.   Calculate Hp cost Based on value tested of $X_{i}$
15.   Violation check with Assert($H_{p}$ > TipH)
16.  }
17. }
\end{lstlisting}

@@

To optimize the CPU resources utilization without modifying the underlying SMT Solver, the Open Multi-Processing (OpenMP) library~\cite{Dagum1998} is used in this present work as a front-end for ESBMC. Fig.~\ref{ESBMC-Multi-core} shows our first approach called ``Multi-core ESBMC''.

\begin{figure}[ht]
	\centering
  \includegraphics[scale=1.0]{figures/esbmc-ss.pdf} 
	\caption{ESBMC-SS Approach.}
	\label{ESBMC-Multi-core}
\end{figure}

@@

\begin{figure}[ht]
	\centering
  \includegraphics[scale=1.0]{figures/esbmc-ps.pdf} 
	\caption{ESBMC-PS Approach. }
	\label{ESBMC-Multi-core-Optimized-Sequential-Approach}
\end{figure}

@@

The most optimized approach applies a parallelized binary search to reduce the amount of steps to be executed in order to find the optimal solution. A controller is designed to return the step to be executed so that the number of verification runs are substantially reduced. The parallelized binary search accomplishes this by splitting the domain of possible values into intervals and then by returning the middle of the largest interval so that two new intervals are created.

\begin{figure}[ht]
	\centering
  \includegraphics[scale=1.0]{figures/esbmc-pb.pdf} 
	\caption{ESBMC-PB Approach.}
	\label{ESBMC-Binary-Approach}
\end{figure}

As an example, given a problem of domain from $1$ to $20$ (see Fig.~\ref{Binary-Step-Calculation}), we firstly create an initial interval from $1$ to $20$. When the next available core asks for a step to be executed, the controller obtains the largest interval, {\it i.e.}, $\left[1,20\right]$, divides it by two, which creates two new intervals ({\it i.e.}, $\left[1,9\right]$ and $\left[11,20\right]$), and returns the middle of the original interval ({\it i.e.}, $10$). The controller also checks whether an interval has less than two elements to avoid creating empty or invalid intervals.

\begin{figure}[ht]
	\centering
  \includegraphics[scale=1.0, height=75px]{figures/Fig4.png}
	\caption{Binary Step Calculation.}
	\label{Binary-Step-Calculation}
\end{figure}

@@

\begin{lstlisting}[caption=Steps Calculation using Intervals.,label=Steps-Calculation-using-Intervals]

01. GetNextStep(){
02.  int largestChunk = -1;
03.  chunk largest;
04.  for each(chunk in chunks){
05.     if(chunk.right - chunk.left > largestChunk){
06.           largestChunk = chunk.right - chunk.left;
07.           largest = chunk;
08.     }
09.   }	
10.   chunks.remove(largest);	
11.   int median = largest.left + floor((largest.right - largest.left) / 2)
12.   if(median > 0){
13.      if(largest.right - largest.left > 1)
14.         chunks.add(new chunk(largest.left, median - 1));	
15.      if(largest.right != largest.left)
16.         chunks.add(new chunk(median + 1, largest.right);
17.    }
18.   return median;
19. }
\end{lstlisting}

\vspace{3 mm}
Note that Algorithm~\ref{Steps-Calculation-using-Intervals} is called from each worker in order to get the next step to execute if it exists; otherwise, either zero or a negative number is returned.
From lines $4$ to $9$, the algorithm finds the largest interval. Then, from the line $10$ the largest interval is removed and the median is calculated in line $11$. After that, two new intervals are created, the left side (in line $14$) and the right side (in line $16$). At the end, the median is returned.

\begin{lstlisting}[caption=Worker sample.,label=worker-sample]

01. step = controller.GetNextStep();
02. int pid = ExecuteStep(step);
03. while(isRunning(pid)){
04.   if(!controller.isNeeded(step))
05.    kill(pid);
06. }     
\end{lstlisting}

\vspace{3 mm}
Algorithm~\ref{worker-sample} describes how the worker starts and monitors ESBMC instances. The algorithm starts by retrieving the step to be executed from the controller (line $1$), then initiates the ESBMC instance and obtains the process \textit{id} from the forked process (line $2$). While the step is being executed, the controller checks whether this step is still needed (line $4$). If not, then the ESBMC instance is killed (line $5$) and the worker is free to initiate another step.

@@

\begin{lstlisting}[caption=Pseudocode describing $\nu$Z.,label=vZ-pseudocode, mathescape]

01.#Initialize Variables
02.  Create vZ context 
03.  Create binary vector (x)
04.  Declare number of nodes, edges and $S_{0}$
05.  Declare hardware cost of each node as array (h) 
06.  Declare software cost of each node as array (s)
07.  Declare communication cost of each edge (c)
08.  Declare transposed incidence matrix graph G (E)
09.#Arithmetic Expressions
10.  SC = s(1-x)
11.  CMC = c*|EX|
12.  Fobj =  x[i] * h[i]
13.#Assert Constraints
14.  Add constraints (SF + CMC <= $S_{0}$)
15.  Add constraints to minimize Fobj
16.  Check Model
17.  Print Result
\end{lstlisting}

@@

\begin{table}[h]
\centering
\caption {Description of Benchmarks.}
\small
\sffamily\footnotesize
\tabulinesep=6pt
\begin{tabular}[c]{m{1.5cm}m{0.8cm}m{0.8cm}m{3.8cm}}
  \toprule[1.5pt]
%  \head{Name} & \head{Nodes} & \head{Edges} & \head{Description}\\
  \midrule
